\documentclass{article}
\begin{document}
So you found this?  Nosing around in the repo?  Welcome to the CSC274 Overachiever's Club!

\section*{First rule of Overachiever's Club}
\begin{center}
    \textbf{First rule of Overachiever's Club is \\\emph{Don't talk about Overachiever's Club}}
\end{center}

Don't tell people how to find this document.  The only hint you can give is to look in the class materials.

\section*{Benefits of being a member of Overachiever's Club}

There is one benefit of being in Overachiever's Club.  You may submit typed notes if you do it as
described below (of course there is a catch).
\begin{itemize}
    \item You must type your work in \LaTeX.
    \item Make your answers blue.  You may do this several ways. Once you figure out how to make your answers blue, you can just do a global search and replace.
    \item Delete the unnecessary vspace* statements after each essay question.
\end{itemize}

Yes.  This is a sneaky way to trick you into learning a little \LaTeX.  
It's not that bad.  You have the base documents in the repository. 
You will only need to modify existing documents.

Here are my hints:
\begin{itemize}
    \item Clone the repo.  That will give you the original .tex files that you may just modify.
    \item You will need two files.  You need the *.tex file and the *.sty file.
    \item The sty file could be a bit tricky.  The way I did it, I only have one file named csc274videonotes.sty.  It is in the Unit00 folder.  I made symbollic links to the original style file.  The link is processed properly if you are on a linux system.  I suspect it also works OK on a Mac because a Mac is BSD.  However, on Windows you have to copy the .sty file into the current directory because the link does not work properly.
    \item The csc274videonotes.sty file already does a usepackage{xcolor} so you do not need to do that.  
    \item If you look at Unit00.tex, you will see that I already changed the color of some answers for you.  Your output should be darker.
    \item Upload your .pdf file generated by pdflatex on Linux.  You are on your own for other OS's
    \item Practice compiling this file.  You don't need it, but this file does not need a .sty file so it removes one potential complication.
\end{itemize}


\end{document}